---
title: "P8105_hw6_qs2200"
author: "Qi Shao"
date: "11/20/2018"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(purrr)
library(modelr)
library(mgcv)
```

##Problem 1

Tidy the data.
```{r problem 1.1}
homi_df = read_csv("./data/homicide-data.csv") 
homi_df = 
  homi_df%>%
  mutate(city_state = str_c(city, ", ", state)) %>%
  janitor::clean_names() %>%
  mutate(homi_solved= ifelse(disposition == "Closed by arrest", 1, 0)) %>%
  filter(!(city_state %in%c("Dallas, TX", "Phoenix, AZ", "Kansas City, MO", "Tulsa, AL"))) %>%
  mutate(victim_race = ifelse(victim_race == "White", "white", "non-white"), victim_age = as.integer(victim_age), victim_race = fct_relevel(victim_race, "white", "non-white")) 
```

```{r problem 1.2}
balti_model = homi_df %>%
  filter(city_state == "Baltimore, MD")

glm( homi_solved ~ victim_age + victim_sex + victim_race, data = balti_model, family = binomial()) %>%
broom::tidy() %>%
mutate(OR_estimate = exp(estimate), OR_conf_low = exp(estimate-qnorm(.975)*std.error), OR_conf_high = exp(estimate+qnorm(.975)*std.error)) %>%
filter(term == "victim_racenon-white") %>%
select(term,OR_conf_low, OR_estimate, OR_conf_high) %>% 
knitr::kable(digits = 3)
```

The result of linear model shows that the adjusted odds ratio of solved homicides in which the victim is non-white estimated to be 0.441 times the odds ratio of homicides in which the victim is white.

```{r problem 1.3, fig.height = 7}

each_city = homi_df %>%
  group_by(city_state) %>%
  nest()

odds_glm = function(df){
  glm( homi_solved ~ victim_age + victim_sex + victim_race, data = df, family =     binomial())  %>%
  broom::tidy() %>%
  mutate(OR_estimate = exp(estimate), OR_conf_low =        exp(estimate-qnorm(.975)*std.error), OR_conf_high = exp(estimate+qnorm(.975)*std.error)) %>%
  filter(term == "victim_racenon-white") %>%
  select(term,OR_conf_low, OR_estimate, OR_conf_high)
}

all_estimate = 
  mutate(each_city, or = map(data, odds_glm)) %>%
  select(city_state, or) %>%
  unnest() %>%
  select(-term)

all_estimate %>%
  mutate(city_state = fct_reorder(city_state, OR_estimate)) %>%
  ggplot(aes(x = city_state,y = OR_estimate)) + 
  geom_point() +
  geom_errorbar(aes(ymin = OR_conf_low,ymax = OR_conf_high))+
  geom_hline(yintercept = 1, alpha = 0.5, color = "red")+
  coord_flip()+
  theme_minimal()+
  labs(title = "Estimate and 95% CI of solving homicides odds ratio for each city", 
         x = "City and State", 
         y = "Solving homicides odds ratio comparing non-white victims to white victims") 
```

From the plot, we can see in most cities in the study, the estimate odds ratio of solving homicides comparing non-white victims to white victims is less than 1. It indicate that in most of the cities, homicides in which the victim is non-white are substantially less likely to be resolved that those in which the victim is white. There are also some cities in which CI of odds ratio including 1, and 3 of them have estimate odds ratio greater than 1. In these cities, homicides in which the victim is non-white are more likely to be resolved that those in which the victim is white.

## Problem 2
### Tidy the data
```{r problem 2.1}
birthweight_df = read_csv("./data/birthweight.csv") 

birthweight_df = janitor::clean_names(birthweight_df) %>%
  mutate(babysex = replace(babysex, babysex == 1, 'male'),
            babysex = replace(babysex, babysex == 2, 'female'),
            babysex = as_factor(babysex),
            frace = replace(frace, frace == 1, 'White'),
            frace = replace(frace, frace == 2, 'Black'),
            frace = replace(frace, frace == 3, 'Asian'),
            frace = replace(frace, frace == 4, 'Puerto Rican'),
            frace = replace(frace, frace == 8, 'Other'),
            frace = replace(frace, frace == 9, 'Unknown'),
            frace = as_factor(frace),
            malform = replace(malform, malform == 0, 'absent'),
            malform = replace(malform, malform == 1, 'present'),
            malform = as_factor(malform),
            mrace = replace(mrace, mrace == 1, 'White'),
            mrace = replace(mrace, mrace == 2, 'Black'),
            mrace = replace(mrace, mrace == 3, 'Asian'),
            mrace = replace(mrace, mrace == 4, 'Puerto Rican'),
            mrace = replace(mrace, mrace == 8, 'Other'),
            mrace = as_factor(mrace)) %>%
  dplyr::select(bwt, everything())

sum(is.na(birthweight_df))
```

There are no missing value in this dataset.

### Propose a regression model

Use backward elimination method to build a regression model, take out non-significant variables one at a time.

```{r problem 2.3}
mult.fit = lm( bwt ~ ., data = birthweight_df)
summary (mult.fit)
step1 = update(mult.fit, . ~ . -pnumsga)
summary(step1)
step2 = update(step1, . ~ . -pnumlbw)
summary(step2)
step3 = update(step2, . ~ . -wtgain)
summary(step3)
step4 = update(step3, . ~ . -malform)
summary(step4)
step5 = update(step4, . ~ . -ppbmi)
summary(step5)
step6 = update(step5, . ~ . -frace)
summary(step6)
step7 = update(step6, . ~ . -momage)
summary(step7)
step8 = update(step7, . ~ . -menarche)
summary(step8)

fit_model1 = lm(bwt ~ babysex + bhead + blength + delwt + fincome + gaweeks + mheight + mrace + parity + ppwt + smoken, data = birthweight_df)
```
backforward



#mult.fit <- lm(bwt ~ ., data=)
#step(mult.fit, direction='backward')

#lm1 = lm( bwt ~ babysex + bhead + blength + delwt + fincome +    gaweeks + mheight + mrace + parity + ppwt + smoken, data = birthweight_df)
#summary(lm1)

leaps(x = birthweight_df[,2], y = birthweight_df[,1], nbest=2, method="Cp")


# Printing the 2 best models of each size, using the adjusted R^2 criterion:
leaps(x = birthweight_df[,2:18], y = surg[,1], nbest=2, method="adjr2")

# Summary of models for each size (one model per size)
b<-regsubsets(Lnsurvival ~ ., data=surg)
   (rs<-summary(b))

# Plots of Cp and Adj-R2 as functions of parameters
par(mar=c(4,4,1,1))
par(mfrow=c(1,2))

plot(2:9, rs$cp, xlab="No of parameters", ylab="Cp Statistic")
abline(0,1)

plot(2:9, rs$adjr2, xlab="No of parameters", ylab="Adj R2")
```{r}
birthweight_df %>%
  modelr::add_residuals(fit_model1) %>% 
  modelr::add_predictions(fit_model1) %>% 
  ggplot(aes(x = pred, y = resid)) + geom_point()

```

```{r}
fit_model2 = lm(bwt ~ blength + gaweeks, data = birthweight_df)
summary(fit_model2)

fit_model3 = lm(bwt ~ bhead + blength + babysex + bhead*blength + bhead*babysex + blength*babysex + bhead*blength*babysex, data = birthweight_df)
summary(fit_model3)

cv_df = 
  crossv_mc(birthweight_df, 100)%>%
  mutate(train = map(train, as_tibble),
         test = map(test, as_tibble)) %>%
  mutate(fit_model1 = map(train, ~lm(bwt ~ babysex + bhead + blength + delwt + fincome + gaweeks + mheight + mrace + parity + ppwt + smoken, data = .x)),
         fit_model2 = map(train, ~lm(bwt ~ blength + gaweeks,data = .x)),
         fit_model3 = map(train, ~lm(bwt ~ bhead + blength + babysex + bhead*blength + bhead*babysex + blength*babysex + bhead*blength*babysex, data = .x))) %>% 
  mutate(rmse_model1 = map2_dbl(fit_model1, test, ~rmse(model = .x, data = .y)),
         rmse_model2 = map2_dbl(fit_model2, test, ~rmse(model = .x, data = .y)),
         rmse_model3 = map2_dbl(fit_model3, test, ~rmse(model = .x, data = .y)))

cv_df %>% 
  dplyr::select(starts_with("rmse")) %>% 
  gather(key = model, value = rmse) %>% 
  mutate(model = str_replace(model, "rmse_", ""),
         model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
         